\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-27 syntax.tex
comments

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{It is not unspecified. I now change it so that it is more clear. It is parametric as well. Just note that when specifying the abstraction `A', the seal `f' has to be specified at the sametime. (Thus I omitted it initially because it is implicitly specified w.r.t. the speicifcation of `f') }
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$, thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

This sealing is the general version of the sealed family implemented in
the plugin. Our plugin will deduce a sealed ``interface'' (which is the "A" in \ruleref{Sig Add}) \YZ{Does this 'interface' correspond to A?}\EDJreply{Yes.}
for a sealed family using a fixed set of rules, but here sealing in
metatheory can be arbitrary local morphism  $\goodTerm{\Gamma , \cC
\sigma}{\_}{A[\pi_1]}$.\YZ{why?}\EDJreply{local morphism is exactly term of this form}
With the definition of sealing judgement in mind, we can see
\ruleref{Sig Add} and \ruleref{Lnkg Add} work exactly as the
implementation. In the implementation, we will have "self__" all around
when defining new fields in our plugin, and this "self__" is exactly the
$A$ in the context of the two fields---in our implementation, sealing
happens only to inductive types (where each inductive type we only know
\mintinline{Coq}{T : Set}).

>>>>

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{It is not unspecified. I now change it so that it is more clear. It is parametric as well. Just note that when specifying the abstraction `A', the seal `f' has to be specified at the sametime. (Thus I omitted it initially because it is implicitly specified w.r.t. the speicifcation of `f') }\YZreply{
  Changed what? I think Lnkg Add and Sig Add were not changed.
  I still don't see how sealing converts \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}
  and how the latter is now used as the abstracted A.
}
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

This sealing is the general version of the sealed family implemented in
the plugin. Our plugin will deduce a sealed ``interface'' (which is the "A" in \ruleref{Sig Add})
for a sealed family using a fixed set of rules, but here sealing in
metatheory can be arbitrary local morphism  $\goodTerm{\Gamma , \cC
\sigma}{\_}{A[\pi_1]}$.
With the definition of sealing judgement in mind, we can see
\ruleref{Sig Add} and \ruleref{Lnkg Add} work exactly as the
implementation. In the implementation, we will have "self__" all around
when defining new fields in our plugin, and this "self__" is exactly the
$A$ in the context of the two fields---in our implementation, sealing
happens only to inductive types (where each inductive type we only know
\mintinline{Coq}{T : Set}).
